Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2023-09-19 Paper/Manuscript.tex
Added information to json files and file reader, changed json file names

\subsection{Accompanying code}
The code  accompanying this paper is written in the Python programming language (v3.10) and is available through GitHub (see \ref{dataavstatement} for code and data availability) together with the data used in the examples. All single ping processing steps with respective figures in the paper can be reproduced by running the main script, \code{main.py}. Reproduction of Fig. \ref{fi:ts_theta_phi}a and Fig. \ref{fi:Fig_Sv_echogram}a requires downloading the original echosounder raw data separately and using the scripts (\code{TSfEchogram.py} and \code{SvfEchogram.py}). Without loss of generality, we use the \ek{} echosounder as an example since it is currently the most commonly used broadband system in the marine ecosystem acoustics field. The test data sets accompanying the code are representative for the data contained in Simrad EK80 raw files. In order to make the code echosounder independent simple json strings are used as input. Detailed information on settings used during data collection are available in the code and the data files on GitHub.

@@

Compensation of echo strength for position in the acoustic beam requires an estimate of the echo arrival angle. This is obtained using the splitbeam method \citep{burdic1991}, which for broadband pules can be implemented with the angle values contained in the complex-valued $\ypc(\samplesymt)$ data, in combination with knowledge of transducer sector geometry. The principle is demonstrated with a transducer that is divided into four quadrants (Fig. \ref{fi:Fig_trd_quad_Impedances}a). In this example the summed signals from four halves (1+2, 2+3, 3+4, 4+1) are calculated as:
\begin{eqnarray}
\label{eq:SumHalves}
y_{\textrm{pc,fore}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,3)+\ypc(\samplesymt,4) \right),\\
y_{\textrm{pc,aft}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,1)+\ypc(\samplesymt,2) \right),\\
y_{\textrm{pc,star}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,1)+\ypc(\samplesymt,4) \right),\\
y_{\textrm{pc,port}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,2)+\ypc(\samplesymt,3) \right),
\end{eqnarray}
%
where fore, aft, star(board), and port indicate the relevant transducer halves.

>>>>

\subsection{Accompanying code}
The code  accompanying this paper is written in the Python programming language (v3.10) and is available through GitHub (see \ref{dataavstatement} for code and data availability) together with the data used in the examples. All single ping processing steps with respective figures in the paper can be reproduced by running the main script, \code{main.py}. Reproduction of Fig. \ref{fi:ts_theta_phi}a and Fig. \ref{fi:Fig_Sv_echogram}a requires downloading the original echosounder raw data separately and using the scripts (\code{TSfEchogram.py} and \code{SvfEchogram.py}). Without loss of generality, we use the \ek{} echosounder as an example since it is currently the most commonly used broadband system in the marine ecosystem acoustics field. The test data sets accompanying the code are representative for the data contained in Simrad EK80 raw files. In order to make the code echosounder independent simple json strings are used as input. Detailed information on settings used during data collection is available in the code and the data files on GitHub.

@@

Compensation of echo strength for position in the acoustic beam requires an estimate of the echo arrival angle. This is obtained using the splitbeam method \citep{burdic1991}, which for broadband pules can be implemented with the angle values contained in the complex-valued $\ypc(\samplesymt)$ data, in combination with knowledge of transducer sector geometry. The principle is demonstrated with a transducer that is divided into four quadrants (Fig. \ref{fi:Fig_trd_quad_Impedances}a). In this example the summed signals from four halves (1+2, 2+3, 3+4, 4+1) are calculated as:
\begin{eqnarray}
\label{eq:SumHalves}
y_{\textrm{pc,fore}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,3)+\ypc(\samplesymt,4) \right),\\
y_{\textrm{pc,aft}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,1)+\ypc(\samplesymt,2) \right),\\
y_{\textrm{pc,star}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,1)+\ypc(\samplesymt,4) \right),\\
y_{\textrm{pc,port}}(\samplesymt) & = & \frac{1}{2} \left( \ypc(\samplesymt,2)+\ypc(\samplesymt,3) \right),
\end{eqnarray}
%
where fore, aft, star(board), and port indicate the relevant transducer halves. In scientific echoshounder data fore-aft angles are often labelled  alongship angles and  port-starboard angles athwartship angles.
